### 2018-05-02 paper/message-passing-design.tex
up
merge algo

To implement our  probabilistic
predictive onion routing mechanism, \name defined two different algorithms to
receive, send messages among users' \squad. For instance,
if Alice wants to send a message \(m\) to Bob, Bob uses the
\([Recv]\) algorithm (See \cref{SPORRecv}) to create a probabilistic onion route \(H_{Bob}\) from
 a set of rendez-vous point to its own devices from its \squad --- all the hops on the route are 
chosen by Bob uniformly at random from its RPS (\view).
 \([Recv]\) returns the \(H_{Bob}\).
PORs have \(L\) layers, and for each layer the number of
alternatives nodes depends of a failure threshold \(\theta\). 
As long as \(\theta\) is not exceeded, alternatives nodes are added in
\(H_{Bob}\) as depicted in \cref{ExtendRoute}. Thus the probability of
failure for the extension is \(1 - (1 - \theta)^L\). In a similar
manner, Alice create an onion route \(H_{Alice}\) to enable Bob to
acknowledge its messages. Bob and Alice exchange then their calculated
PORs (i.e. H_{Bob} andH_{Alice}), using an
out-of-band channel, \eg using one device of their \squad (See
Fig.~\ref{fig:file-exchange}~\ding{182}).

@@

Once Alice get the \(H_{Bob}\), Alice uses \([Send]\) at some
later time to send the message to Bob using any of her devices from
its \squad (See \cref{SPORSend}). First, \([Send]\) extends the route
\(H_{Bob}\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \([Send]\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \([Fwd]\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_{Bob} = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \([Store]\) sub function 
(\cref{SPORRecv}).

%The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
%    is intended for the local node and \(c_m\) is instead sent to disk using 
%    \(\Store\) (\cref{SPORRecv}).%

@@

    % \Require{%
    %   $H$ is a header of the form \(D\concat H'\) or \(D\concat \top\), where 
    %   \(D\) is a set of device addresses.
    %   $\pk_D$ is the public key of device set $D$.
    % }

\begin{figure}

% <<<<<<< HEAD
%   \framebox{\begin{minipage}{0.96\linewidth}
% =======
%       \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
%       \State $D\concat C_H\gets H_\rdv$
%       \For{$d\in D$}
%         \Comment{Uniformly randomly chosen}
%         \If{$d\method \Fwd[C_H, m] \neq \bot$}
%           \State \Return $\top$
%         \EndIf
%       \EndFor
%       \State \Return $\bot$
%     \EndFunction
%   \end{algorithmic}
%   %\end{minipage}}

%   % \vspace{0.3em}
%   % %\framebox{\begin{minipage}{0.96\linewidth}
% >>>>>>> 028fcc4225628a4b1d8b1b48a64b7975d11021ab
\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
\scriptsize
    \Function{\ExtendRoute}{$H, L$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \CreateOnionLayer[]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction
  \vspace{0.3em}
    \Function{\CreateOnionLayer}{}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $D\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in D} p_d > \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{ExtendRoute}%
    \scriptsize
    The \(\ExtendRoute\) algorithm extends a route \(H\)
  }
\end{figure}

@@

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}
\scriptsize
    \Require{%
      $D$ is the set of alternative recipient devices.
    }
    \Function{[\Recv]}{$D$}
      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
      \State \Return $H_\rdv$
        \Comment{Give to sender out-of-bound.}
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{SPORRecv}%
\scriptsize
    The \(\SPOR[\Recv]\) algorithm prepares the recipient for receiving a file.
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}
\scriptsize
    \Require{%
      $m$ is the message to be sent,
      $H$ is the onion-route given by the recipient.
    }
    \Function{[\Send]}{$H,m$}
      \State $H\gets \ExtendRoute[H, L, \theta]$
      \State $D\concat C_H\gets H_\rdv$
      \For{$d\in D$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H, m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{SPORSend}%
    \scriptsize
    The \(\SPOR[\Send]\) algorithm 
  }
\end{figure}

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}
\scriptsize
    \Require{$\sk$ is the private key-pair of the current node.}
    \Function{\SPOR[\Fwd]}{$C_H, m$}
      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
    \Function{\Store}{$m$}
      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{SPORFwd}%
    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\).%
  }
\end{figure}

>>>>

To implement our  probabilistic
predictive onion routing mechanism, \name defined two different algorithms to
receive, send messages among users' \squad. For instance,
if Alice wants to send a message \(m\) to Bob, Bob uses the
\([Recv]\) algorithm (See \cref{SPORFwd}) to create a probabilistic onion route \(H_{Bob}\) from
 a set of rendez-vous point to its own devices from its \squad --- all the hops on the route are 
chosen by Bob uniformly at random from its RPS (\view).
 \([Recv]\) returns the \(H_{Bob}\).
PORs have \(L\) layers, and for each layer the number of
alternatives nodes depends of a failure threshold \(\theta\). 
As long as \(\theta\) is not exceeded, alternatives nodes are added in
\(H_{Bob}\) as depicted in \cref{ExtendRoute}. Thus the probability of
failure for the extension is \(1 - (1 - \theta)^L\). In a similar
manner, Alice create an onion route \(H_{Alice}\) to enable Bob to
acknowledge its messages. Bob and Alice exchange then their calculated
PORs (i.e. H_{Bob} andH_{Alice}), using an
out-of-band channel, \eg using one device of their \squad (See
Fig.~\ref{fig:file-exchange}~\ding{182}).

@@

Once Alice get the \(H_{Bob}\), Alice uses \([Send]\) at some
later time to send the message to Bob using any of her devices from
its \squad (See \cref{SPORFwd}). First, \([Send]\) extends the route
\(H_{Bob}\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \([Send]\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \([Fwd]\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_{Bob} = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \([Store]\) sub function 
(\cref{SPORFwd}).

%The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
%    is intended for the local node and \(c_m\) is instead sent to disk using 
%    \(\Store\) (\cref{SPORFwd}).%

@@

\begin{figure}
\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
\scriptsize
    \Function{\ExtendRoute}{$H, L$}
      \If{$L\leq 0$}
        \State \Return $H$
      \EndIf
      \State $D\gets \CreateOnionLayer[]$
      \State $H\gets D\concat \DeBEenc[\mpk, D, H]$
      \State \Return $\ExtendRoute[H, L-1, \theta]$
    \EndFunction
  \vspace{0.3em}
    \Function{\CreateOnionLayer}{}
      \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
      \State $D\gets \{(d, \pk_d, p_d)\}$
      \While{$\prod_{d\in D} p_d > \theta$}
        \State $(d, \pk_d, p_d)\gets \GetRandomPeer$
        \State $D\gets D\cup \{(d, \pk_d, p_d)\}$
      \EndWhile
      \State \Return $D$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{ExtendRoute}%
    \scriptsize
    The \(\ExtendRoute\) algorithm extends a route \(H\)
  }
\end{figure}

@@

\begin{figure}
  \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}
\scriptsize
    \Require{%
      $D$ is the set of alternative recipient devices.
    }
    \Function{\Recv}{$D$}
      \State $H_\rdv\gets \ExtendRoute[D\concat \top, L, \theta]$
      \State \Return $H_\rdv$
        \Comment{Give to sender out-of-bound.}
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
%   \caption{\label{SPORFwd}%
% \scriptsize
%     The \(\Recv\) algorithm prepares the recipient for receiving a file.
%   }
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}
\scriptsize
    \Require{%
      $m$ is the message to be sent,
      $H$ is the onion-route given by the recipient.
    }
    \Function{\Send}{$H,m$}
      \State $H\gets \ExtendRoute[H, L, \theta]$
      \State $D\concat C_H\gets H_\rdv$
      \For{$d\in D$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H, m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  % \caption{\label{SPORFwd}%
  %   \scriptsize
  %   The \(\Recv\), \(\Send\) and \(\Fwd\) algorithms.
  % }
 % \framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}
\scriptsize
    \Require{$\sk$ is the private key-pair of the current node.}
    \Function{\Fwd}{$C_H, m$}
      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
    \Function{\Store}{$m$}
      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  \end{minipage}}
  \caption{\label{SPORFwd}%
    \scriptsize
    The \(\Recv\) (prepares the recipient for receiving a file), \(\Send\) and \(\Fwd\) (forwards \(m\) down the route \(H\)) algorithms.
  }
\end{figure}
